Beta Diversity through Time and Space

### 2020-09-25 analyses/abund_div_GAM.Rmd
refined plotting

#check.gamViz(weighted_fl_abundance.2010)
#weighted_fl_abundance.2010.sum <- summary(weighted_fl_abundance.2010)
#print(plot(weighted_fl_abundance.2010, allTerms = TRUE), pages = 4)
#weighted_fl_abundance.2010.ck <- check2D(weighted_fl_abundance.2010, x1 = "yday", x2 = "elev.mean")

@@

### Extract predictions
```{r message=FALSE}
# Function to build data set over which to generate predictions
newdata_build <- function(dat, y) {

@@

  ## species list
  spp <- dat %>%
    filter(year == y) %>%
    select(bb.sp) %>%
    unique()

@@

  newdata <- tibble(seq_yday, seq_elev) %>% # combine seqs into data frame
    complete(seq_yday, seq_elev) %>% # get all possible values
    crossing(spp) %>% # get all possible combos with species
    select(yday = seq_yday, elev.mean = seq_elev, bb.sp) # rename columns to match the original model inputs
}

@@

predict_pool.FL <- bind_rows(predict2010.FL, predict2011.FL, predict2012.FL) %>%
  mutate(date = as_date(yday),
         subject = factor(rep("FL", n())))
predict_pool.FL.sqrt <- bind_rows(predict2010.FL.sqrt, predict2011.FL.sqrt, predict2012.FL.sqrt) %>%
  mutate(date = as_date(yday),
         subject = factor(rep("FL", n())))
predict_pool.FL.bin <- bind_rows(predict2010.FL.bin, predict2011.FL.bin, predict2012.FL.bin) %>%
  mutate(date = as_date(yday),
         subject = factor(rep("FL", n())))

predict2010.BB <- predict_func(bb_abund.2010, newdata2010.BB, 2010)
predict2011.BB <- predict_func(bb_abund.2011, newdata2011.BB, 2011)
predict2012.BB <- predict_func(bb_abund.2012, newdata2012.BB, 2012)
predict_pool.BB <- bind_rows(predict2010.BB, predict2011.BB, predict2012.BB) %>%
  mutate(date = as_date(yday),
         subject = factor(rep("BB", n())),
         pred = log(pred))

predict_pool <- bind_rows(predict_pool.FL, predict_pool.BB)
predict_pool.sqrt <- bind_rows(predict_pool.FL.sqrt, predict_pool.BB)
predict_pool.bin <- bind_rows(predict_pool.FL.bin, predict_pool.BB)

# Subset predictions
predict_major <- filter(predict_pool, 
                           bb.sp %in% c("bss", "pasc", "prat", "soro", "wurf")) %>%
  mutate(bb.sp = case_when(
    bb.sp == "bss" ~ "B. ss.",
    bb.sp == "pasc" ~ "B. pasc",
    bb.sp == "prat" ~ "B. prat",
    bb.sp == "soro" ~ "B. soro",
    bb.sp == "wurf" ~ "B. wurf"
  ))

predict_major.sqrt <- filter(predict_pool.sqrt, 
                           bb.sp %in% c("bss", "pasc", "prat", "soro", "wurf")) %>%
  mutate(bb.sp = case_when(
    bb.sp == "bss" ~ "B. ss.",
    bb.sp == "pasc" ~ "B. pasc",
    bb.sp == "prat" ~ "B. prat",
    bb.sp == "soro" ~ "B. soro",
    bb.sp == "wurf" ~ "B. wurf"
  ))

predict_major.bin <- filter(predict_pool.bin, 
                           bb.sp %in% c("bss", "pasc", "prat", "soro", "wurf")) %>%
  mutate(bb.sp = case_when(
    bb.sp == "bss" ~ "B. ss.",
    bb.sp == "pasc" ~ "B. pasc",
    bb.sp == "prat" ~ "B. prat",
    bb.sp == "soro" ~ "B. soro",
    bb.sp == "wurf" ~ "B. wurf"
  ))

predict_highelev <- filter(predict_pool, 
                              bb.sp %in% c("pyre", "mend", "mont")) %>%
  mutate(bb.sp = case_when(
    bb.sp == "pyre" ~ "B. pyre",
    bb.sp == "mend" ~ "B. mend",
    bb.sp == "mont" ~ "B. mont"
  ))

predict_highelev.sqrt <- filter(predict_pool.sqrt, 
                                   bb.sp %in% c("pyre", "mend", "mont")) %>%
  mutate(bb.sp = case_when(
    bb.sp == "pyre" ~ "B. pyre",
    bb.sp == "mend" ~ "B. mend",
    bb.sp == "mont" ~ "B. mont"
  ))

predict_highelev.bin <- filter(predict_pool.bin, 
                                  bb.sp %in% c("pyre", "mend", "mont")) %>%
  mutate(bb.sp = case_when(
    bb.sp == "pyre" ~ "B. pyre",
    bb.sp == "mend" ~ "B. mend",
    bb.sp == "mont" ~ "B. mont"
  ))

predict_minor <- filter(predict_pool, 
                           bb.sp %in% c("gers", "hort", "hypn","jone", "lapi", "muci")) %>%
  mutate(bb.sp = case_when(
    bb.sp == "gers" ~ "B. gers",
    bb.sp == "hort" ~ "B. hort",
    bb.sp == "hypn" ~ "B. hypn",
    bb.sp == "jone" ~ "B. jone",
    bb.sp == "lapi" ~ "B. lapi",
    bb.sp == "muci" ~ "B. muci"
  ))

predict_minor.sqrt <- filter(predict_pool.sqrt, 
                                bb.sp %in% c("gers", "hort", "hypn","jone", "lapi", "muci")) %>% 
  mutate(bb.sp = case_when(
    bb.sp == "gers" ~ "B. gers",
    bb.sp == "hort" ~ "B. hort",
    bb.sp == "hypn" ~ "B. hypn",
    bb.sp == "jone" ~ "B. jone",
    bb.sp == "lapi" ~ "B. lapi",
    bb.sp == "muci" ~ "B. muci"
  ))

predict_minor.bin <- filter(predict_pool.bin, 
                               bb.sp %in% c("gers", "hort", "hypn","jone", "lapi", "muci")) %>% 
  mutate(bb.sp = case_when(
    bb.sp == "gers" ~ "B. gers",
    bb.sp == "hort" ~ "B. hort",
    bb.sp == "hypn" ~ "B. hypn",
    bb.sp == "jone" ~ "B. jone",
    bb.sp == "lapi" ~ "B. lapi",
    bb.sp == "muci" ~ "B. muci"
  ))
```

### Visualize
```{r}
#### Major
ggplot(predict_major, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_major.png", height = 5, width = 11, units = "in")

ggplot(predict_major.sqrt, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))
ggsave("./output/GAM_major_sqrt.png")

ggplot(predict_major.bin, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))
ggsave("./output/GAM_major_bin.png")

#### High Elev
ggplot(predict_highelev, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_highelev.png", height = 5, width = 11, units = "in")

ggplot(predict_highelev.sqrt, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_highelev_sqrt.png", height = 5, width = 11, units = "in")

ggplot(predict_highelev.bin, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_highelev_bin.png", height = 5, width = 11, units = "in")

#### Minor
ggplot(predict_minor, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_minor.png", height = 5, width = 11, units = "in")

ggplot(predict_minor.sqrt, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_minor_sqrt.png", height = 5, width = 11, units = "in")

ggplot(predict_minor.bin, aes(date, elev.mean, fill = pred)) +
  geom_raster() +
  geom_contour(aes(z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  #facet_grid(bb.sp + subject ~ year) +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_minor_bin.png", height = 5, width = 11, units = "in")
```

>>>>

#check.gamViz(weighted_fl_abundance.2010)
#weighted_fl_abundance.2010.sum <- summary(weighted_fl_abundance.2010)
#saveRDS(weighted_fl_abundance.2010.sum, file = "./output/weighted_fl_abundance_2010.rds")
#print(plot(weighted_fl_abundance.2010, allTerms = TRUE), pages = 4)
#weighted_fl_abundance.2010.ck <- check2D(weighted_fl_abundance.2010, x1 = "yday", x2 = "elev.mean")

@@

# We might be interested in whether and where (in time*elev) a given pair of smooths differs from each other. It might only make sense to do this, though, if we first normalized abundance for each species; otherwise, the differences may be driven by differences in overall abundance. I'm not sure the species random effect takes care of that.
```{r}
# 2010 pasc vs prat
plotDiff.mgcv.smooth.2D(s1 = sm(bb_abund.2010, 10), s2 = sm(bb_abund.2010, 11)) +
  l_pvRaster() + 
  l_pvContour()

plotDiff.mgcv.smooth.2D(s1 = sm(weighted_fl_abundance.2010, 12), 
                        s2 = sm(weighted_fl_abundance.2010, 13)) +
  l_pvRaster() + 
  l_pvContour()

# 2010 pasc vs prat
plotDiff.mgcv.smooth.2D(s1 = sm(bb_abund.2011, 10), s2 = sm(bb_abund.2011, 11)) +
  l_pvRaster() + 
  l_pvContour()

# 2010 pasc vs prat
plotDiff.mgcv.smooth.2D(s1 = sm(bb_abund.2012, 10), s2 = sm(bb_abund.2012, 11)) +
  l_pvRaster() + 
  l_pvContour()
```

### Extract predictions
```{r message=FALSE}
### Species names and such for plotting
species_names <- cbind(c("bss", "pasc", "prat", 
                         "soro", "wurf", "hort", 
                         "pyre", "mend", "mont", 
                         "gers", "hypn","jone", 
                         "lapi", "muci", "psit", 
                         "humi"),
                       c("B. sensu-strictu", "B. pascuorum", "B. pratorum", 
                         "B. soroensis", "B. wurflenii", "B. hortorum",
                         "B. pyrenaeus", "B. mendax", "B. monticola",
                         "B. gerstaeckeri", "B. hypnorum", "B. jonellus", 
                         "B. lapidarius", "B. mucidus", "B. psithyrus", 
                         "B. humilis"),
                       c("B. ss.", "B. pasc.", "B. prat.", 
                         "B. soro.", "B. wurf.", "B. hort.",
                         "B. pyre.", "B. mend.", "B. mont.",
                         "B. gers.", "B. hypn.", "B. jone.", 
                         "B. lapi.", "B. muci.", "B. psit.", 
                         "B. humi"),
                       c("major", "major", "major", 
                         "major", "major", "common", 
                         "high elev.", "high elev.", "high elev.",
                         "minor", "minor", "common", 
                         "minor", "minor", "common", 
                         "minor")
                       ) %>%
  as.data.frame() %>%
  as_tibble() %>%
  dplyr::select(bb.sp = 1, species.name = 2, species.abb = 3, abund.class = 4)

BB_samples <- net %>%
  mutate(year = year(date),
         date = as_date(yday(date))) %>%
  left_join(site_data) %>%
  select(year, date, elev.mean) %>%
  mutate(subject = rep("BB", n()),
         sampled = rep(TRUE, n())) %>%
  unique()

FL_samples <- survey %>%
  ungroup() %>%
  mutate(year = year(date),
         date = as_date(yday(date))) %>%
  unique() %>%
  left_join(site_data) %>%
  select(year, date, elev.mean) %>%
  mutate(subject = rep("FL", n()),
         sampled = rep(TRUE, n())) %>%
  unique()

samples <- bind_rows(BB_samples, FL_samples)

# Function to build data set over which to generate predictions
newdata_build <- function(dat, y) {

@@

  ## species list
  spp <- dat %>%
    filter(year == y) %>%
    dplyr::select(bb.sp) %>%
    unique()

@@

  newdata <- tibble(seq_yday, seq_elev) %>% # combine seqs into data frame
    complete(seq_yday, seq_elev) %>% # get all possible values
    tidyr::crossing(spp) %>% # get all possible combos with species
    dplyr::select(yday = seq_yday, elev.mean = seq_elev, bb.sp) # rename columns to match the original model inputs
}

@@

predict_pool.FL <- bind_rows(predict2010.FL, predict2011.FL, predict2012.FL) %>%
  mutate(subject = factor(rep("FL", n())))

predict_pool.FL.sqrt <- bind_rows(predict2010.FL.sqrt, predict2011.FL.sqrt, predict2012.FL.sqrt) %>%
  mutate(subject = factor(rep("FL", n())))

predict_pool.FL.bin <- bind_rows(predict2010.FL.bin, predict2011.FL.bin, predict2012.FL.bin) %>%
  mutate(subject = factor(rep("FL", n())))

predict2010.BB <- predict_func(bb_abund.2010, newdata2010.BB, 2010)
predict2011.BB <- predict_func(bb_abund.2011, newdata2011.BB, 2011)
predict2012.BB <- predict_func(bb_abund.2012, newdata2012.BB, 2012)
predict_pool.BB <- bind_rows(predict2010.BB, predict2011.BB, predict2012.BB) %>%
  mutate(subject = factor(rep("BB", n()))) %>%
  mutate(pred = log(pred))

predict_pool <- bind_rows(predict_pool.FL, predict_pool.BB) %>%
  left_join(species_names) %>%
  mutate(date = as_date(yday))
predict_pool.sqrt <- bind_rows(predict_pool.FL.sqrt, predict_pool.BB) %>%
  left_join(species_names) %>%
  mutate(date = as_date(yday))
predict_pool.bin <- bind_rows(predict_pool.FL.bin, predict_pool.BB) %>%
  left_join(species_names) %>%
  mutate(date = as_date(yday))
```

### Visualize
```{r}
# Convex hull function: https://cran.r-project.org/web/packages/ggplot2/vignettes/extending-ggplot2.html

StatChull <- ggproto("StatChull", Stat,
  compute_group = function(data, scales) {
    data[chull(data$x, data$y), , drop = FALSE]
  },

  required_aes = c("x", "y")
)

stat_chull <- function(mapping = NULL, data = NULL, geom = "polygon",
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatChull, data = data, mapping = mapping, geom = geom, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}
##

#### Major
ggplot() +
  geom_raster(data = filter(predict_pool, abund.class == "major"), 
              aes(date, elev.mean, fill = pred), 
              interpolate = TRUE) +
  geom_contour(data = filter(predict_pool, abund.class == "major"),
               aes(date, elev.mean, z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  stat_chull(data = samples, aes(date, elev.mean), fill = NA, 
             color = "deeppink", size = 0.25) +
  facet_grid(year ~ species.abb + subject, scales = "free_y") +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme_gray(6) +
  theme(axis.text.x = element_text(angle = 90, size = 5, vjust = 0.5)) 
ggsave("./output/GAM_major.png", height = 2.5, width = 6.5, units = "in")
ggsave("./output/GAM_major.pdf", height = 2.5, width = 6.5)

#### High Elev
ggplot() +
  geom_raster(data = filter(predict_pool, abund.class == "high elev."), 
              aes(date, elev.mean, fill = pred), 
              interpolate = TRUE) +
  geom_contour(data = filter(predict_pool, abund.class == "high elev."),
               aes(date, elev.mean, z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  stat_chull(data = samples, aes(date, elev.mean), fill = NA, 
             color = "deeppink", size = 0.25) +
  facet_grid(year ~ species.abb + subject, scales = "free_y") +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme_gray(6) +
  theme(axis.text.x = element_text(angle = 90, size = 5, vjust = 0.5)) 
ggsave("./output/GAM_highelev.png", height = 2.5, width = 6.5, units = "in")
ggsave("./output/GAM_highelev.pdf", height = 2.5, width = 6.5)

#### Minor
ggplot() +
  geom_raster(data = filter(predict_pool, abund.class == "minor"), 
              aes(date, elev.mean, fill = pred), 
              interpolate = TRUE) +
  geom_contour(data = filter(predict_pool, abund.class == "minor"),
               aes(date, elev.mean, z = pred), color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  stat_chull(data = samples, aes(date, elev.mean), fill = NA, 
             color = "white", size = 0.5, linetype = "dashed") +
  facet_grid(year ~ bb.sp + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_minor.png", height = 5, width = 11, units = "in")

### Just for kicks and chortles, let's see what happens if we scale the prediction for each species, then average across species to create a single plot.
predict_pool.mean <- predict_pool %>%
  group_by(bb.sp, species.name, species.abb, year, subject) %>%
  mutate(pred.norm = scale(pred)) %>%
  group_by(date, elev.mean, year, subject, abund.class) %>%
  summarize(pred.mean = mean(pred.norm))

ggplot() +
  geom_raster(data = predict_pool.mean, 
              aes(date, elev.mean, fill = pred.mean), 
              interpolate = TRUE) +
  geom_contour(data = predict_pool.mean,
               aes(date, elev.mean, z = pred.mean), 
               color = "black", size = 0.25) +
  scale_fill_viridis_c(name = "log(abund.)") +
  stat_chull(data = samples, aes(date, elev.mean), fill = NA, 
             color = "white", size = 0.5, linetype = "dashed") +
  facet_grid(year ~ abund.class + subject) +
  xlab("Date") +
  ylab("Elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
ggsave("./output/GAM_mean.png", height = 5, width = 11, units = "in")
```

### 2020-09-25 analyses/beta_diversity.Rmd
refined plotting

### Prepare environment
```{r message=FALSE, warning=FALSE}
library(lubridate)
library(sf)
library(gdm)
library(bipartite)
library(vegan)
library(mgcv)
library(mgcViz)
library(see)
library(tidyverse)
```

@@

# Elevation diff within 1 wk time diff
ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                !metric.class %in% c("OS.partition", "WN.partition") &
                yday.diff <= 7), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.1, pch = 16, size = 1) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  scale_color_manual(values = p, name = "partition") +
  xlab("Elevation difference") +
  ylab("β-diversity")
ggsave("./output/beta_elev.png", height = 4.5, width = 6.5, units = "in")

# Time diff within 250 m elev diff
ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                !metric.class %in% c("OS.partition", "WN.partition") &
                elev.diff <= 250), 
       aes(yday.diff, value, color = metric)) +
  geom_point(alpha = 0.1, pch = 16, size = 1) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  scale_color_manual(values = p, name = "partition") +
  xlab("Elevation difference") +
  ylab("β-diversity")
ggsave("./output/beta_time.png", height = 4.5, width = 6.5, units = "in")
```

>>>>

### Prepare environment
```{r message=FALSE, warning=FALSE}
library(lubridate)
library(sf)
library(gdm)
library(patchwork)
library(bipartite)
library(vegan)
library(mgcv)
library(mgcViz)
library(see)
library(tidyverse)
```

@@

# Elevation diff within 1 wk time diff
p1 <- ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                !metric.class %in% c("OS.partition", "WN.partition") 
                #& yday.diff <= 7
                ), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.03, pch = 16, size = 0.25) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 6)) +
  facet_grid(metric.class ~ year1) +
  scale_color_manual(values = p, name = "partition") +
  xlab("Elevation difference (m)") +
  ylab("β-diversity")
ggsave("./output/beta_elev.png", height = 4.5, width = 6.5, units = "in")

# Time diff within 250 m elev diff
p2 <- ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                !metric.class %in% c("OS.partition", "WN.partition")
               # & elev.diff <= 250
                ), 
       aes(yday.diff, value, color = metric)) +
  geom_point(alpha = 0.03, pch = 16, size = 0.25) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 6)) +
  facet_grid(metric.class ~ year1) +
  scale_color_manual(values = p, name = "partition") +
  xlab("Time difference (days)") +
  ylab("β-diversity") + 
  theme(legend.position="none")
ggsave("./output/beta_time.png", height = 4.5, width = 6.5, units = "in")

png("./output/beta_stack.png", width = 6.5, height = 6.5, units = "in", res = 300)
p1 / p2 + plot_annotation(tag_levels = c("A", "B", "C")) + plot_layout(guides = "collect")
dev.off()

WN.hist <- ggplot(filter(beta_mit_data, year1 == year2 &
                           site1 != site2 &
                           metric == "WN"), 
                aes(value)) +
  geom_histogram() +
  scale_y_continuous(trans="pseudo_log", breaks = c(0, 10, 100, 1000, 10000)) +
  geom_vline(aes(xintercept = mean(value))) +
  facet_wrap(~year1) +
  xlab("Total β-diversity") +
  ylab("Site-date pairs")
ggsave("./output/WN_hist.png", width = 6.5, height = 3, units = "in")
```
